---
title: "Journal (reproducible report)"
author: "Sandeep Madhusudan"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post

Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

## Data Aquisition
```{r}
# WEBSCRAPING ----


# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing

# 1.1 COLLECT PRODUCT TYPES ----
url_home          <- "https://www.radon-bikes.de/"
xopen(url_home)
html_home         <- read_html(url_home)
bike_family_tbl <- html_home %>%
html_nodes(css = ".megamenu__item > a") %>%  
html_attr('href') %>%  
discard(.p = ~stringr::str_detect(.x,"wear")) %>%  
enframe(name = "position", value = "cat_subcat_url") %>%  
  
mutate(family_id = str_glue("https://www.radon-bikes.de{cat_subcat_url}bikegrid"))
bike_family_tbl

 
# 2.0 COLLECT BIKE DATA ----

bike_category_url <- bike_family_tbl$family_id[1]
xopen(bike_category_url)
html_bike_category  <- read_html(bike_category_url)

bike_name_tbl        <- html_bike_category %>%
html_nodes(css = ".m-bikegrid__info .a-heading--small") %>%
html_text() %>%


enframe(name = "position", value = "name")
bike_name_tbl 

bike_price_tbl <- html_bike_category %>%
html_nodes(css = ".m-bikegrid__price.currency_eur .m-bikegrid__price--active") %>%  
html_text() %>% 
enframe(name = "position", value = "price")
bike_price_tbl

model_price_tbl <- left_join(bike_name_tbl, bike_price_tbl)%>% 
select(name, price)
model_price_tbl
```


### third level header

Here's an even lower level header

# Data Visualization
Challenge 1
```{r}
library(tidyverse)
library(ggthemes)
library(lubridate)
library(ggrepel)

## DATA PREPARATION

library(tidyverse)
covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")


covid_data_2020_cumulative_cases <- covid_data_tbl %>%
  select(countriesAndTerritories, month, year, cases) %>% 
  set_names(c("country", "month", "year", "cases")) %>%
  
  # Selecting columns to focus on and adding a month column
  
  filter(year == "2020") %>%
  filter(country %in%  c("Germany", "Spain", "France","United_States_of_America","United_Kingdom"))  %>%
  
  # Grouping by month, and summarizing cases
  group_by(month,country) %>%
  summarize(cases = sum(cases)) %>% 
  ungroup() %>%
  group_by(country) %>%
  mutate (cases = cumsum(cases)) %>%
  ungroup() %>%

  mutate(cumulative_cases = scales::dollar(cases, big.mark = ".", 
                                   decimal.mark = ",", 
                                   prefix = "", 
                                   suffix = ""))

## PLOTTING
# Canvas
covid_data_2020_cumulative_cases  %>%
  ggplot(aes(x = month, y = cases, color = country)) +

  # Geometries
  geom_line(size = 1) +
  
  # geom_label(data = covid_data_2020_cumulative_cases %>% select(cases) %>% max(cases))+
  # geom_label(aes(x=month, y=cases, label=cumulative_cases) , 
  #            data = covid_data_2020_cumulative_cases %>% slice(which.max(cases)),
  #            vjust = -0.2, 
  #            hjust = 0.1) +
  
  geom_label_repel(aes(x=month, y=cases, label=cumulative_cases) , 
                   data = covid_data_2020_cumulative_cases %>% slice(which.max(cases)),
                    vjust = 0.5, 
                    hjust = 2.5,color = "#08306B")+

  # Formatting
  expand_limits(y = 0) +
 
  scale_x_continuous(breaks = covid_data_2020_cumulative_cases$month,
                     labels = month(covid_data_2020_cumulative_cases$month, label = T)) +
  
  scale_y_continuous(breaks = seq(0e6, 16e6, by = 2e6),
                     labels = scales::dollar_format(scale = 1/1e6,
                                                    prefix = "",
                                                    suffix = "M")) +
  labs(
    title = "COVID-19 confirmed cases worldwide",
    x = "Year 2020",
    y = "Cumulative Cases",
    color = "Country"
  )  +
  
  theme_light() +
  theme(title = element_text(face = "bold", color = "#08306B"),
        legend.position  = "bottom",
        axis.text.x = element_text(angle = 45))
```

Challenge 2 
```{r}
cat("\014")
library(ggplot2)
library(dplyr)
library(tidyverse)
library(ggthemes)
library(lubridate)
library(ggrepel)
library(maps)
library(readr)
library(scales)
## DATA PREPARATION
covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")


covid_mortality_rate <- covid_data_tbl %>%
  select(countriesAndTerritories, deaths, popData2019) %>% 
  set_names(c("country", "deaths", "population")) %>%
  
  # Selecting columns to focus on and adding a month column
  mutate(mortality_rate = deaths/population)%>%
  mutate(across(country, str_replace_all, "_", " ")) %>%
  mutate(country = case_when(
    
    country == "United Kingdom" ~ "UK",
    country == "United States of America" ~ "USA",
    country == "Czechia" ~ "Czech Republic",
    TRUE ~ country
  )) %>%
  
  group_by(country) %>%
  summarize(deaths=sum(deaths),population=max(population),mortality_rate = sum(mortality_rate)) %>%
  ungroup() 
 

world <- map_data("world")

covid_world_mortality_rate <- left_join(x = world, y = covid_mortality_rate, by=c("region" = "country")) 

ggplot(covid_world_mortality_rate, aes(x=long, y=lat, group = group, fill = (mortality_rate))) + 
  geom_polygon(colour = "white") +
  scale_fill_continuous(low = "dodgerblue",
                        high = "black",
                        guide="colorbar",
                        labels=percent,
                        limits = c(0, .0015)) +
   
  
  
  theme_bw() +
  labs(fill = "Mortality Rate" ,
       title = "Confirmed COVID-19 deaths relative to the size of population", 
       subtitle = "More than 1.5 Million confirmed COVID-19 deaths worldwide",
       x="long", 
       y="lat") 



  # scale_y_continuous(breaks=c()) +
  # scale_x_continuous(breaks=c()) +
  # theme()
```





When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.